---
title: "DataVisualization"
output: html_document
date: "2025-03-10"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(root.dir = "/Users/aparnapetluri/Desktop/107")
```

Uploading the simulation data set

```{r}
source("00_requirements.R") #uploading libraries
save(cars_data, file = "data_for_visualization.RData")
load("data_for_visualization.RData")
```

## Plotting a few visualizations to see how simulated features relate to the brand choice

## Histograms

Histogram of popularity distribution based on the brand name.

```{r}
png("Popularity.png", width = 800, height = 400)
par(mfrow = c(1,2))
# Histogram for Ferrari Popularity
hist(cars_data$popularity[cars_data$Brand_binary == 0], 
     main = "Popularity Distribution for Ferrari", 
     xlab = "Popularity", col = "red")
# Histogram for McLaren Popularity
hist(cars_data$popularity[cars_data$Brand_binary == 1], 
     main = "Popularity Distribution for McLaren", 
     xlab = "Popularity", col = "blue")
dev.off()
par(mfrow = c(1,1))
hist(cars_data$popularity[cars_data$Brand_binary == 0], 
     main = "Popularity Distribution for Ferrari", 
     xlab = "Popularity", col = "red")
hist(cars_data$popularity[cars_data$Brand_binary == 1], 
     main = "Popularity Distribution for McLaren", 
     xlab = "Popularity", col = "blue")
```

From this, I can see that McLaren's popularity distribution is normal, while Ferrari's is slightly left-skewed.

Trying the same to see if there is a difference in horsepower, as performance is one of my predictor variables for why people prefer one brand over another.

```{r}
# Histogram for Ferrari Horsepower
hist(cars_data$horsepower[cars_data$Brand_binary == 0], 
     main = "Horsepower Distribution for Ferrari", 
     xlab = "Horsepower", col = "red")

# Histogram for McLaren Horsepower
hist(cars_data$horsepower[cars_data$Brand_binary == 1], 
     main = "Horsepower Distribution for McLaren", 
     xlab = "Horsepower", col = "blue")
```

The mean of McLaren's horsepower is higher, yet the graph shows higher variability as well.

Attempting with price:

```{r}
png("Price.png", width = 800, height = 400)
par(mfrow = c(1,2))
# Histogram for Ferrari Price
hist(cars_data$price[cars_data$Brand_binary == 0], 
     main = "Price Distribution for Ferrari", 
     xlab = "Price", col = "red")

# Histogram for McLaren Price
hist(cars_data$price[cars_data$Brand_binary == 1], 
     main = "Price Distribution for McLaren", 
     xlab = "Price", col = "blue")
dev.off()
par(mfrow = c(1,1))

hist(cars_data$price[cars_data$Brand_binary == 0], 
     main = "Price Distribution for Ferrari", 
     xlab = "Price", col = "red")

hist(cars_data$price[cars_data$Brand_binary == 1], 
     main = "Price Distribution for McLaren", 
     xlab = "Price", col = "blue")

```

McLaren seems to have higher prices as well!

## Scatterplots

Does horsepower seem to have an impact on popularity?

```{r}
# Histogram for Popularity with Horsepower Price
png("PopHorsepower.png", width = 800, height = 400)
plot(cars_data$horsepower, cars_data$popularity, 
     main = "Popularity vs Horsepower", 
     xlab = "Horsepower", 
     ylab = "Popularity", 
     col = ifelse(cars_data$Brand_binary == 0, "red", "blue"))
legend("topright", legend = c("Ferrari", "McLaren"), 
       col = c("red", "blue"), pch = 19)
dev.off()

plot(cars_data$horsepower, cars_data$popularity, 
     main = "Popularity vs Horsepower", 
     xlab = "Horsepower", 
     ylab = "Popularity", 
     col = ifelse(cars_data$Brand_binary == 0, "red", "blue"))
legend("topright", legend = c("Ferrari", "McLaren"), 
       col = c("red", "blue"), pch = 19)
```

There does not seem to be any correlation between horsepower and popularity. Additionally, there are no remarks about the different brands either.

Does price have an impact on popularity?

```{r}
plot(cars_data$price, cars_data$popularity, 
     main = "Popularity vs Price", 
     xlab = "Price", 
     ylab = "Popularity", 
     col = ifelse(cars_data$Brand_binary == 0, "red", "blue"))
legend("topright", legend = c("Ferrari", "McLaren"), 
       col = c("red", "blue"), pch = 19)
```

Based on this, I am seeing no correlation between popularity and price.

## Boxplot

Popularity vs. Brand Name

Before doing logistic regression, I wish to gain an understanding of if there are any correlations between the name of the brand and popularity. Since popularity is out of 4 (categorical), I would like to see this using a boxplot rather than a scatterplot!

```{r}
png("brandpop.png", width = 800, height = 400)
boxplot(cars_data$Brand_binary, cars_data$popularity, 
     main = "Popularity vs Brand Name", 
     xlab = "Brand (0 = Ferrari, 1 = McLaren)", 
     ylab = "Popularity")   
dev.off()
boxplot(cars_data$Brand_binary, cars_data$popularity, 
     main = "Popularity vs Brand Name", 
     xlab = "Brand (0 = Ferrari, 1 = McLaren)", 
     ylab = "Popularity") 
```
